\TITLE

### 2024-08-14 paper/main.tex
update comparision table

\begin{table*}
\centering
\newcommand{\YES}{\cellcolor{green!50}Yes}
\newcommand{\YESBUT}{\cellcolor{green!25}Yes*}
\newcommand{\ID}{\cellcolor{green!25}Identity}
\newcommand{\PSEUDO}{\cellcolor{green!35}Pseudonym}
\newcommand{\ANON}{\cellcolor{green!50}Anonymity}
\newcommand{\NO}{\cellcolor{red!50}No}
\newcommand{\TTP}{\cellcolor{red!50}TTP}
\newcommand{\BC}{\cellcolor{green!50}BC}
\caption{Comparison of related works. The notation \textit{Pseudonymity} means that the anonymity is based on the assumption that the pseudonym is not linked to the real identity; \textit{TTP} means that the protocol uses a trusted third party; \textit{BC} means that the protocol uses a public blockchain; \textit{YES*} means that the protocol provides the feature but is based on strong or impractical assumptions.}
\label{tab:comparison}
\setlength{\tabcolsep}{3pt}

\begin{tabular}{cccccc}

\noalign{\smallskip}\hline\noalign{\smallskip}
Protocol & Fair exchange & Anonymity & Dispute resolution & Trust & Physical delivery \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\cite{zhangPracticalFairExchangeEPayment2006} (2006) & \YES & \YESBUT & \YES & \TTP & \YES \\
\cite{mohammedalarajFairnessPhysicalProducts2012} (2012) & \YESBUT & \NO & \YES & \TTP & \YES \\
Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} (2017) & \YES & \PSEUDO & \NO & \BC & \YES \\
\cite{hinarejosSolutionSecureCertified2019} (2019) & \YES & \NO & \NO & \BC & \NO \\
Themis~\cite{mengThemisDecentralizedEscrow2019} (2019) & \YES & \NO & \YES & \BC & \NO \\
PPPDCP~\cite{birjoveanuTwoPartyECommerceProtocols2022} (2022) & \YES & \YES & \YES & \TTP & \YES \\
This paper & \YES & \YES & \YES & \BC & \YES \\
\noalign{\smallskip}\hline

>>>>

\begin{table*}
\centering
\newcommand{\YES}{\cellcolor{green!50}Yes}
\newcommand{\YESBUT}{\cellcolor{green!25}Yes*}
\newcommand{\ID}{\cellcolor{green!25}Identity}
\newcommand{\PSEUDO}{\cellcolor{green!35}Pseudonym}
\newcommand{\ANON}{\cellcolor{green!50}Anonymity}
\newcommand{\NO}{\cellcolor{red!50}No}
\newcommand{\TTP}{\cellcolor{red!50}TTP}
\newcommand{\OffTTP}{\cellcolor{orange!50}Offline TTP}
\newcommand{\OffBC}{\cellcolor{yellow!50}BC \& Offline TTP}
\newcommand{\BC}{\cellcolor{green!50}BC}
\caption{Comparison of related works. Category Definitions: \textit{E-commerce:} Secure online transactions for physical goods; \textit{Private Delivery System:} Methods ensuring fair and anonymous delivery of physical products; \textit{Certified email:} Secure exchange of certified electronic mail with proof of receipt; \textit{Digital escrow:} Decentralized escrow services for secure digital currency transactions. The notation \textit{Pseudonymity} means that the anonymity is based on the assumption that the pseudonym is not linked to the real identity; \textit{TTP} means that the protocol relies on a trusted third party in every transaction; \textit{Offline TTP} means that the protocol relies on a trusted third party only to resolve disputes; \textit{BC} means that the protocol uses a public blockchain; \textit{YES*} means that the protocol provides the feature but is based on strong or impractical assumptions.}
\label{tab:comparison}
\setlength{\tabcolsep}{3pt}

\begin{tabular}{ccccccc}

\noalign{\smallskip}\hline\noalign{\smallskip}
Protocol & Scenario & Fair exchange & Anonymity & Dispute resolution & Trust & Physical delivery \\
\noalign{\smallskip}\hline\noalign{\smallskip}
Zhang et al. \cite{zhangPracticalFairExchangeEPayment2006} (2006) & E-commerce & \YES & \YESBUT & \YES & \TTP & \YES  \\
Alaraj et al.\cite{mohammedalarajFairnessPhysicalProducts2012} (2012) & E-commerce & \YESBUT & \NO & \YES & \OffTTP & \YES \\
Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} (2017) & Private Delivery System & \YES & \PSEUDO & \NO & \BC & \YES \\
Hinarejos et al.\cite{hinarejosSolutionSecureCertified2019} (2019) & Certified email & \YES & \NO & \NO & \BC & \NO \\
Themis~\cite{mengThemisDecentralizedEscrow2019} (2019) & Digital escrow & \YES & \NO & \YES & \BC & \NO \\
PPPDCP~\cite{birjoveanuTwoPartyECommerceProtocols2022} (2022) & E-commerce & \YES & \YES & \YES & \TTP & \YES \\
This paper & E-commerce & \YES & \YES & \YES & \OffBC & \YES \\
\noalign{\smallskip}\hline
